Disease Knowledge Transfer across Neurodegenerative Diseases

### 2019-10-09 paper/pres/poster-dkt.tex
last changes for poster

\heading{Aim}\;\;\;\;Infer progression of multimodal biomarkers in rare neurodegenerative diseases (NDs) by leveraging larger datasets of common NDs.

@@

\begin{figure}[H]

\includegraphics[width=\columnwidth]{DKT_intuition}

@@

  \end{subfigure}
  \begin{subfigure}{0.49\columnwidth}
   \centering
%    \vspace{-1.2em}
   \fnt{2. Dysfunction trajectory modelled using region-specific biomarkers}\\
   $ y_{ijk} = g( \gamma_{ij}^{k} ; \theta_k) + N(0,\epsilon_k) $
%    \vspace{0.6em}
%    \includegraphics[width=\textwidth]{dysfuncEvol}
  \end{subfigure}

 \includegraphics[width=\columnwidth]{disease_knowledge_transfer_poster.pdf}
  \fnt{3. Extend to multiple subjects, biomarkers and diseases}\\
 $ p(\boldsymbol{y}|\theta, \lambda, \beta , \epsilon) = \prod_{(i,j,k) \in \Omega} p(y_{ijk}|\theta_k, \lp, \beta_{i}) $
 \end{figure}

@@

\begin{itemize}
 \item Dementia Research Center cohort: MRI scans from 76 PCA, 67 tAD, 87 controls for training, 10 PCA with DTI for validation.
 \item TADPOLE dataset (ADNI) split into three subgroups with different progressions: 21 hippocampal, 35 cortical, 27 subcortical.
%  \item Synthetic dataset mimicking the cohorts above: 50 subjects with "synthetic PCA", 100 subjects with "synthetic AD".
\end{itemize}

>>>>

\heading{Aim}\;\;\;\;Infer progression of multimodal biomarkers in rare neurodegenerative diseases (NDs) by leveraging larger datasets of common, related variants.

@@

\begin{figure}[H]
\centering
\includegraphics[width=1\columnwidth]{DKT_intuition}

@@

  \end{subfigure}
  \begin{subfigure}{0.49\columnwidth}
   \centering
%    \vspace{-1.2em}
   \fnt{2. Dysfunction trajectory modelled using region-specific biomarkers}\\
   $ y_{ij}^k = g( \gamma_{ij}^{k} ; \theta_k) + N(0,\epsilon_k) $\\
%    \fnt{$y_{ijk}$ = measure in subject $i$, visit $j$, region $k$.}

%    \vspace{0.6em}
%    \includegraphics[width=\textwidth]{dysfuncEvol}
  \end{subfigure}
% \vspace{-2em}

 \includegraphics[width=\columnwidth,trim=0 0 0 00,clip]{disease_knowledge_transfer_poster.pdf}

  \fnt{3. Extend to multiple subjects, biomarkers and diseases}\\
 $ p(\boldsymbol{y}|\theta, \lambda, \beta , \epsilon) = \prod_{(i,j,k) \in \Omega} p(y_{ij}^k|\theta_k, \lp, \beta_{i}) $
 \end{figure}

@@

\begin{itemize}
 \item TADPOLE dataset (ADNI) split into three subgroups with different progressions: 21 hippocampal, 35 cortical, 27 subcortical.
\item Dementia Research Center cohort: MRI scans from 76 PCA, 67 tAD, 87 controls for training, 10 PCA with DTI for validation.
%  \item Synthetic dataset mimicking the cohorts above: 50 subjects with "synthetic PCA", 100 subjects with "synthetic AD".
\end{itemize}
